### 2010-04-07 docs/architecture/architecture.tex
typo
MG intro

\section{Multigrid}
\subsection{Special Bottom Solver}
We have a special bottom solver type that greatly speeds up large problems
and speeds up smaller problems to a lesser degree.
In fact, you should use this bottom solver whenever possible, because I
have yet to find a case that performs worse than our standard bottom solver.
What this special solver essentially does is take the data from the coarsest 
level of the original multigrid V-cycle and copy it onto a new grid structure 
with the same number of total cells in each direction, but with a fewer number of larger 
grids.  A new V-cycle begins from this point, 
so we are essentially coarsening this ``new'' problem.
Now, the coarsest level of the multigrid V-cycle in the ``new'' problem has 
fewer cells and fewer grids as compared to the original coarsest level.

@@

{\bf Example 2:} A 2D problem with $96\times 384$ cells into $48^2$ grids, i.e., 
there is a $2\times 8$ block of $48^2$ grids.  The coarsest level of the multigrid 
V-cycle contains $2\times 8$ grids that have $3^2$ cells, so the entire problem 
domain has $6\times 24$ cells.  We see that $n=1$, so the program aborts since this grid
structure is not appropriate for the fancy bottom solver.

>>>>

\section{Multigrid}

MAESTRO uses the multigrid solver to enforce the divergence constraint
both on the half-time edge-centered advective velocities (the ``MAC
projection'') and on the final cell-centered velocities (the ``HG
projection'').  For the MAC projection, since the velocity data is
edge-centered (the MAC grid), the projection is cell-centered.  For
the HG projection, since the velocity data is cell-centered, the
projection is node-centered.  \MarginPar{should draw a figure} The multigrid solver performs a number
of V-cycles until the residual drops by 10-12 orders-of-magnitude.
There are several options that affect how the multigrid solver
behaves, which we describe below.

\subsection{Special Bottom Solver}
We have a special bottom solver type that greatly speeds up large problems
and speeds up smaller problems to a lesser degree.
In fact, you should use this bottom solver whenever possible, because I
have yet to find a case that performs worse than our standard bottom solver.
What this special solver essentially does is take the data from the coarsest 
level of the original multigrid V-cycle and copy it onto a new grid structure 
with the same number of total cells in each direction, but with a fewer number of larger 
grids.  A new V-cycle begins from this point, 
so we are essentially coarsening this ``new'' problem.
Now, the coarsest level of the multigrid V-cycle in the ``new'' problem has 
fewer cells and fewer grids as compared to the original coarsest level.

@@

{\bf Example 2:} A 2D problem with $96\times 384$ cells divided into $48^2$ grids, i.e., 
there is a $2\times 8$ block of $48^2$ grids.  The coarsest level of the multigrid 
V-cycle contains $2\times 8$ grids that have $3^2$ cells, so the entire problem 
domain has $6\times 24$ cells.  We see that $n=1$, so the program aborts since this grid
structure is not appropriate for the fancy bottom solver.
